########################### **Set Up** ########################### 
---
title: "Main"
output:       
  bookdown::pdf_document2: default
  bookdown::word_document2: default
  bookdown::html_document2: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE,
                      fig.retina = 3)
```

10:32
```{r packages & functions}
library(tidyverse)
library(bookdown)
sum_sq <- function(df, measure, group) {
  df %>% group_by({{ group }}) %>% 
    summarise(ss = sum(({{measure}} - mean({{measure}}))^2))
}

data_summary <- function(df, measure, group)  {
  df %>% 
   group_by({{ group }}) %>% 
   summarise(mean_index = mean({{ measure }}),
            n = length({{ measure }}),  sd = sd({{ measure }}), se = sd/sqrt(n))
  }
```

########################### **Data Import** ###########################
chaff <- read.delim("~/University/Year 3/Data Science/chaff/raw_data/chaff.txt") %>%
  janitor::clean_names()
View(chaff)sum_sq(chaff2, mass, sex)
data_summary(chaff2, mass, sex)

########################## **Data Tidying** ###########################
chaff2 <- chaff %>% 
  pivot_longer(names_to = "sex", 
               values_to = "mass",
               cols = c(1,2))
               
########################### **Data Analysis** ########################### 
sum_sq(chaff2, mass, sex)
chaffsummary <- data_summary(chaff2, mass, sex)

########################### **Data Saving** ########################### 
file <-  "Processed_data/chaff2.txt"
write.table(chaff2, 
            file, 
            quote = FALSE,
            row.names = FALSE)
file <-  "Processed_data/chaffsummary.txt"
write.table(chaffsummary, 
            file, 
            quote = FALSE,
            row.names = FALSE)